GAM

### 2023-08-25 Analysis/Appendix/E1_Appendix.qmd
re-render

```{r setupAe1, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

>>>>

```{r setupAe1, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test")  |>
  select(id,condit,bandInt,vb,vx,dist,sdist,bandType,tOrder)
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

### 2023-08-25 Analysis/e1_test.qmd
re-render

result <- test_summary_table(test, "dist", mfun = list(mean = mean, median = median, sd = sd))
result$constant
result$varied

@@

```{r}
#| label: tbl-e1-bmm-dist
#| tbl-cap: "Experiment 1. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
#contrasts(test$condit)

# contrasts(test$vb)

modelName <- "e1_testDistBand_RF_5K"
e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
                      data=test,file=paste0(here::here("data/model_cache",modelName)),
                      iter=5000,chains=4)
GetModelStats(e1_distBMM) |> kable(escape=F,booktabs=T)

@@

e1_distBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |>
  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
    ylab("Predicted Deviation") + xlab("Velocity Band")+
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(test$vb), 
                     limits = c(0, 1400)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
```

@@

```{r}
#| label: tbl-e1-bmm-vx
#| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
#| tbl-subcap: ["Model fit to all 6 bands", "Model fit to 3 extrapolation bands"]
e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
GetModelStats(e1_vxBMM ) |> kable(escape=F,booktabs=T)

@@

See @tbl-e1-bmm-vx for the full model results. The estimated coefficient for training condition (β = 146, 95% CI [35.96, 254.70]) suggests that the varied group tends to produce harder throws than the constant group. Most relevant to the issue of discrimination is the slope on Velocity Band (β = 0.69, 95% CI [.59, .77]). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands. The slope coefficient (β = 0.69 ) also seems in accordance with an examination of @tbl-e1-test-nf-vx, which shows that average x-velocity fell within the range of the target band for four out of six of the bands ($4/6$=.67). The estimate for the interaction between slope and condition (β = -.12, 95% CI [-.25, 0.00]), suggests that the varied condition had significantly lower slopes than did the constant group. This difference is depicted visually in @fig-e1-bmm-bx.

@@

condEffectsPlot <- ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + stat_halfeye(alpha=.2) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  scale_x_continuous(breaks = c(100, 350, 600), 
                     labels = levels(test$vb)[1:3], 
                     limits = c(0, 1000)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

e1_vxBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |>
  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + stat_halfeye(alpha=.2) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +

  ylab("Predicted X Velocity") + xlab("Band")+
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(test$vb), 
                     limits = c(0, 1400)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

e1_extrap_VxBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600))) |>
  gather_emmeans_draws() |>
  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + stat_halfeye(alpha=.2) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +

  ylab("Predicted X Velocity") + xlab("Band")+
  scale_x_continuous(breaks = c(100, 350, 600), 
                     labels = levels(test$vb)[1:3], 
                     limits = c(0, 1000)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

@@

indv_coefs <- coef(e1_vxBMM)$id |> 
  as_tibble(rownames="id") |> 
  select(id, starts_with("Est")) |>
  left_join(e1Sbjs, by=join_by(id) ) |> 
  group_by(condit) |> 
  mutate(rank = rank(desc(Estimate.bandInt)),
         intErrorRank=rank((Est.Error.Intercept)),
         bandErrorRank=rank((Est.Error.bandInt)),
         nCond = n()) |> arrange(intErrorRank) |> ungroup()

@@

random_effects <- e1_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1500) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

cd <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt) |>
  mutate(Slope=bandInt_RF+b_bandInt) |> group_by(id)

cdMed <- cd |> group_by(id) |> median_qi(Slope)  |> 
  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)

cdMed %>% 
  group_by(condit) %>%  
  reframe(enframe(quantile(Slope, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "Slope")) |> 
  pivot_wider(names_from=quantile,values_from=Slope,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()
```

```{r}
#| label: fig-e1-slope-dist
#| fig-cap: Slope estimates by participant - ordered from lowest to highest within each condition. 
#| fig-height: 9
#| fig-width: 10

cdMed %>% ggplot(aes(y=rankSlope, x=Slope,fill=condit,color=condit)) + 
  geom_pointrange(aes(xmin=.lower , xmax=.upper)) + 
  labs(x="Estimated Slope", y="Participant")  + facet_wrap(~condit)

# cdMed %>% ggplot(aes(x=Slope)) + 
#   stat_halfeye(alpha=.5) +facet_wrap(~condit)

# cdMed |>  ggplot(aes(x = condit, y = Slope,fill=condit)) +
#     stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
#     stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
#   geom_jitter()
#   labs(x="Band", y="Deviation From Target")

@@

```{r}
#| label: fig-e1-indv-slopes
#| fig-cap: Subset of Varied and Constant Participants with the largest estimated slope values. Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution. Colored points and intervals at each band represent the empirical median and 95% HDI. 
#| fig-height: 11

nTop <- 2

combined_df <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt) |>
  right_join(new_data_grid, by = join_by("id")) |> 
  mutate(
    fixed_effects = b_Intercept +
      (bandInt * b_bandInt) +
      condit_dummy * b_conditVaried + 
      (bandInt * condit_dummy) * `b_conditVaried:bandInt` ,  
    random_effects = Intercept + bandInt_RF,  # Assuming random effects for intercept and bandInt
    estimate = (b_Intercept + Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`
  )

combined_df |> 
  filter(id %in% (indv_coefs |> filter(rank<=nTop) |> pull(id)) )  |> 
  group_by(id, bandInt) |>
  sample_n(200) |>
  ggplot(aes(x=bandInt,y=estimate)) + 
  geom_abline(aes(intercept=Intercept+b_Intercept, slope=bandInt_RF+b_bandInt), color="grey50", alpha=.1) +
  geom_abline(data=indv_coefs |> 
                filter(id %in% (indv_coefs |> filter(rank<=nTop) |> pull(id))),aes(intercept=Estimate.Intercept,slope=Estimate.bandInt),color="red") +
  stat_pointinterval(data=test |> filter(id %in% (indv_coefs |> filter(rank<=nTop) |> pull(id))), aes(x=bandInt,y=vx, color=vb)) +
  facet_nested_wrap(vars(condit,id),ncol = 2) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(test$vb), 
                     limits = c(0, 1400)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +  ylab("X Velocity") + xlab("Band")

combined_df |> indv_model_plot(indv_coefs, testAvg, rank_variable=Estimate.bandInt,n_sbj=4,"max")
combined_df |> indv_model_plot(indv_coefs, testAvg, rank_variable=Estimate.bandInt,n_sbj=4,"min")

@@

```{r}
#| label: fig-e1-indv-slopes-small
#| fig-cap: Subset of Varied and Constant Participants with the smallest estimated slope values. Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution. Colored points and intervals at each band represent the empirical median and 95% HDI. 
#| fig-height: 11

nTop <- 2

combined_df |> 
  filter(id %in% (indv_coefs |> filter(rank>nCond-nTop) |> pull(id)) )  |> 
  group_by(id, bandInt) |>
  sample_n(200) |>
  ggplot(aes(x=bandInt,y=estimate)) + 
  geom_abline(aes(intercept=Intercept+b_Intercept, slope=bandInt_RF+b_bandInt), color="grey50", alpha=.1) +
  geom_abline(data=indv_coefs |> 
                filter(id %in% (indv_coefs |> filter(rank>nCond-nTop) |> pull(id))),aes(intercept=Estimate.Intercept,slope=Estimate.bandInt),color="red") +
  stat_pointinterval(data=test |> filter(id %in% (indv_coefs |> filter(rank>nCond-nTop) |> pull(id))), aes(x=bandInt,y=vx, color=vb)) +
  facet_nested_wrap(vars(condit,id),ncol = 2) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(test$vb), 
                     limits = c(0, 1400)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +  ylab("X Velocity") + xlab("Band")

@@

## Acknowledgments {.appendix}

I am grateful for the insightful comments offered by the anonymous peer reviewers at Books & Texts. The generosity and expertise of one and all have improved this study in innumerable ways and saved me from many errors; those that inevitably remain are entirely my own responsibility.

>>>>

result <- test_summary_table(test, "dist", mfun = list(mean = mean, median = median, sd = sd))
result$constant
result$varied
```

::: {layout-ncol=2}

```{r}
#| label: tbl-e1-bmm-dist
#| tbl-cap: "Experiment 1. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"

#contrasts(test$condit) 
#contrasts(test$vb)
modelName <- "e1_testDistBand_RF_5K"
e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
                      data=test,file=paste0(here::here("data/model_cache",modelName)),
                      iter=5000,chains=4)
GetModelStats(e1_distBMM) |> kable(escape=F,booktabs=T)

@@

:::

@@

condEffects <- function(m){
  m |> ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + stat_halfeye(alpha=.2) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
  ylab("Predicted X Velocity") + xlab("Band")
}

e1_distBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |>
 condEffects()+
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(test$vb), 
                     limits = c(0, 1400)) 
```

@@

```{r}
#| label: tbl-e1-bmm-vx
#| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
#| tbl-subcap: ["Model fit to all 6 bands", "Model fit to 3 extrapolation bands"]
#| layout-ncol: 2
#| echo: fenced
e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
GetModelStats(e1_vxBMM ) |> kable(escape=F,booktabs=T)

@@

See @tbl-e1-bmm-vx for the full model results. The estimated coefficient for training condition (β = 146, 95% CI [35.96, 254.70]) suggests that the varied group tends to produce harder throws than the constant group. Most relevant to the issue of discrimination is the slope on Velocity Band (β = 0.69, 95% CI [.59, .77]). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands. The slope coefficient (β = 0.69 ) also seems in accordance with an examination of @tbl-e1-test-nf-vx, which shows that average x-velocity fell within the range of the target band for four out of six of the bands ($4/6$=.67). The estimate for the interaction between slope and condition (β = -.12, 95% CI [-.25, 0.00]), suggests that the varied condition had significantly lower slopes than did the constant group. This difference is depicted visually in @fig-e1-bmm-vx.

@@

e1_vxBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |> 
  condEffects() +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(test$vb), 
                     limits = c(0, 1400))

e1_extrap_VxBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600))) |>
  gather_emmeans_draws() |>
  condEffects() +
  scale_x_continuous(breaks = c(100, 350, 600), 
                     labels = levels(test$vb)[1:3], 
                     limits = c(0, 1000))

@@

indv_coefs <- coef(e1_vxBMM)$id |> 
  as_tibble(rownames="id") |> 
  select(id, starts_with("Est")) |>
  left_join(e1Sbjs, by=join_by(id) )

@@

random_effects <- e1_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1000) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

 indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt) |>
  right_join(new_data_grid, by = join_by("id")) |> 
  mutate(
    Slope = bandInt_RF+b_bandInt,
    estimate = (b_Intercept + Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`
  )

  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope)  |> 
  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)

  indvSlopes |> reframe(enframe(quantile(Slope, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "Slope")) |> 
  pivot_wider(names_from=quantile,values_from=Slope,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()

@@

```{r}
#| label: fig-e1-bmm-bx2
#| fig-cap: Slope estimates by participant - ordered from lowest to highest within each condition. 
#| fig-height: 9
#| fig-width: 10

  indvSlopes |> ggplot(aes(y=rankSlope, x=Slope,fill=condit,color=condit)) + 
  geom_pointrange(aes(xmin=.lower , xmax=.upper)) + 
  labs(x="Estimated Slope", y="Participant")  + facet_wrap(~condit)

@@

```{r}
#| label: fig-e1-indv-slopes
#| fig-cap: Subset of Varied and Constant Participants with the largest estimated slope values. Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution. Colored points and intervals at each band represent the empirical median and 95% HDI. 
#| fig-height: 11
nSbj <- 3
indvDraws  |> indv_model_plot(indv_coefs, testAvg, rank_variable=Estimate.bandInt,n_sbj=nSbj,"max")
indvDraws |> indv_model_plot(indv_coefs, testAvg, rank_variable=Estimate.bandInt,n_sbj=nSbj,"min")

@@

### 2023-08-25 Analysis/methods.qmd
re-render

```{r setup}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,gghalves,patchwork,ggforce,ggdist)
e1 <- readRDS(here("data/e1_07-27-23.rds"))
source(here("Functions/Display_Functions.R"))

@@

```{dot}
//| label: fig-simple
//| fig-cap: "Experimental Design. Constant and Varied participants complete different training conditions."
//| fig-width: 8.0
//| fig-height: 2.5
//| fig-responsive: false
digraph {
  graph [layout = dot, rankdir = LR]

@@

>>>>

```{r setup}
source(here::here("Functions", "packages.R"))
e1 <- readRDS(here("data/e1_08-04-23.rds")) 
e2 <- readRDS(here("data/e2_08-04-23.rds")) 
e3 <- readRDS(here("data/e3_08-04-23.rds"))

@@

```{dot}
//| label: fig-design-e1
//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
//| fig-width: 8.0
//| fig-height: 2.5
//| fig-responsive: false
digraph {
  graph [layout = dot, rankdir = LR]

@@

## HTW Task
* need to create a demo version without consent form. And maybe separate windows for the different versions.

Experimental Task for the HTW Project. Programmed in Javascript, and making use of phaser.js.

```{r out.width = "70%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
knitr::include_graphics(here::here("images/2023-04-19-16-20-55.png"))
```

<!-- ![](images/2023-04-19-16-20-55.png) -->
<!-- `r knitr::include_graphics(here::here("images/2023-04-19-16-20-55.png"))` -->

## Live Task Demo

Check the box at the bottom of the consent form, and then click Start Experiment.

![HTW_Task](https://pcl.sitehost.iu.edu/tg/HTW/HTW_Index_Of.html){width="900" height="800"}

### 2023-08-25 Misc/Visuals_Interactives/model_viz.qmd
re-render

@@

```{r}
library(ggplot2)

@@

```{r}
# Load the visNetwork package
library(visNetwork)

@@

`r knitr::include_graphics(("gaussian_curve_input_node_1.png"))`

```{r}
grViz("digraph causal {
                      	# Nodes
                      	node [imagescale=true,shape = reactangle, fontname = Arial, style = filled]
                      	iv   [label = 'TRT', fillcolor = '#7FC97F']
                      	me   [label = 'Mediator', shape = ellipse]
                      	dv   [label = 'DLQI', fillcolor = '#7FC97F']

@@

@@

svgDataUrl = "data:image/svg+xml;base64,"
grViz('
digraph {
  node[imagescale=true, shape=circle, width=4, height=4,fontname="sans-serif",penwidth=0]
  a[label=<<FONT POINT-SIZE="10">Transaction</FONT><BR/><FONT POINT-SIZE="36"><B>TRNA</B></FONT>>,image="gaussian_curve_input_node_1.png"]
  b[label=<<FONT POINT-SIZE="10">Transaction</FONT><BR/><FONT POINT-SIZE="18"><B>TRNB</B></FONT>>,image="${svgDataUrl}"]
  c[label=<<FONT POINT-SIZE="10">Transaction</FONT><BR/><FONT POINT-SIZE="24"><B>TRNC</B></FONT>>,image="${svgDataUrl}"]
  a -> b
  a -> c
}')

>>>>

### Alt ggplot 2

@@

### Alt ggplot 3
```{r}
library(ggplot2)

@@

```{r}
#| eval: false

# Load the visNetwork package
library(visNetwork)

@@

```{r}
#| eval: false
grViz("digraph causal {
                      	# Nodes
                      	node [imagescale=true,shape = reactangle, fontname = Arial, style = filled]
                      	iv   [label = 'TRT', fillcolor = '#7FC97F']
                      	me   [label = 'Mediator', shape = ellipse]
                      	dv   [label = 'DLQI', fillcolor = '#7FC97F']

@@

```{r}
#| eval: false

@@

svgDataUrl = "data:image/svg+xml;base64,"
grViz('
digraph {
  node[imagescale=true, shape=circle, width=4, height=4,fontname="sans-serif",penwidth=0]
  a[label=<<FONT POINT-SIZE="10">Transaction</FONT><BR/><FONT POINT-SIZE="36"><B>TRNA</B></FONT>>,image="${svgDataUrl}"]
  b[label=<<FONT POINT-SIZE="10">Transaction</FONT><BR/><FONT POINT-SIZE="18"><B>TRNB</B></FONT>>,image="${svgDataUrl}"]
  c[label=<<FONT POINT-SIZE="10">Transaction</FONT><BR/><FONT POINT-SIZE="24"><B>TRNC</B></FONT>>,image="${svgDataUrl}"]
  a -> b
  a -> c
}')

### 2023-08-25 Misc/gam_discrim.qmd
re-render

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,mgcv,data.table)
e1 <- readRDS(here("data/e1_08-04-23.rds"))
source(here("Functions/Display_Functions.R"))

>>>>

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,mgcv,data.table)
e1 <- readRDS(here("data/e1_08-21-23.rds"))
source(here("Functions/Display_Functions.R"))
